Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-14 paper.tex
Mainly comments on the paper
And I think the UMatrix should be moved to Section 3, giving it some more weight. Besides, UMatrix is done for exploratory data analysis and to examine the problem, so it corresponds to "problem description". It is really _not_ part of data processing, because you don't extract any conclusion that excludes or includes variables (I think). Please @amorag check this out.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again?
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

@@

@@

First, after the editorial company has provided the raw data (extracted directly from its database), a preprocessing method has been performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. Moreover, the initial set of variables (presented in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to use just those that can be known in advance when a new book is launched, i.e. \textit{pre-sales data}.

Then, a Feature Selection (FS) process \cite{kittler1986feature} has been carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to discard `noisy' (non-useful) features \cite{Krishnapuram2004}. The aim of these algorithms is exploring the space of attributes to find out which subset of them yields the best results in a classification or prediction problem.
  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
methods.
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

\begin{table}
\caption{Considered pre-sales features and their types. It also shows the names of the variables used in the applied methods.}
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & Input/Output\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

@@

Once a dataset has been composed it must be preprocessed, i.e. it should be revised in order to fix the existing errors (such as wrong or duplicated patterns), or to complete (or address) the absence of information, for instance. The aim is looking for the correctness, homogeneity and completeness of the data.

@@

Moreover, the algorithm running times grow with the number of features, and thus 
making the algorithm impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually applied in these kind of situations, having two ways of performance \cite{kittler1986feature}: feature extraction and feature selection. 
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

@@

Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus it is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.

In addition, in order to reduce the dimensionality of the input data and to choose an appropriate set of variables, the Self-Organizing Map (SOM) \cite{kohonen1998} method has been also applied.

Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that uses an unsupervised training algorithm and which, through a process called self-organisation, configures the output units into a topological representation of the original data. It tries to imitate the self-organisation done in the sensory cortex of the human brain, where neighbouring neurons are activated by similar stimulus. SOM belongs to a general class of neural network methods, which are non-linear regression techniques that can be trained to learn or find relationships between inputs and outputs or to organise data so as to disclose so far unknown patterns or structures. It is usually used as a clustering/classification tool or used to find unknown relationships between a set of variables that describe a problem. The main property of the SOM is that it makes a nonlinear projection from a high-dimensional data space (one dimension per variable) on a regular, low-dimensional (usually 2D) grid of neurons, called units.
SOM is further processed using Ultsch method \cite{UmatUlts}, the Unified distance matrix (U-matrix), which uses SOM's codevectors (vectors of variables of the problem) as data source and generates a matrix where each component is a distance measure between two adjacent neurons. It allows us to visualise any multi-variated dataset in a two-dimensional display, so we can detect topological relations among neurons and infer about the input data structure. High values in the U-matrix represent a frontier region between clusters, and low values represent a high degree of similarities among neurons on that region, clusters.

SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) with high training sample concentration and fewer where the samples are scarce. 
%FERGU: mencionarlo en la intro

>>>>

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again? - JJ
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

@@

% This section is too short and really does not describe the problem
% to its full extent. First, it should say if some of these variables
% were discarded for some reason. Group the variables we have in those
% available to publisher and those that can be used afterwards. And
% then give an idea of the complexity of the problem and how difficult
% it should be to find a solution - JJ

@@

First, after the editorial company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
Then, a Feature Selection (FS) process \cite{kittler1986feature} has
been carried out, as it is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}. The aim of these
% Did you know there were noisy features? Why? 
% You should include in the previous section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ 
algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem. 
  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
methods.  
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & Input/Output\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  editorial + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

@@

Once a dataset has been composed it must be preprocessed, i.e. it
should be revised in order to fix the existing errors (such as wrong
or duplicated patterns), or to complete (or address) the absence of
information, for instance. The aim is looking for the correctness,
homogeneity and completeness of the data. % useless paragraph - JJ

%You need to lay out to the reader what you are going to do here. In
%order to reach objective x, we need to do y, that is why we use
%z. After using z, we prove that we have done y and thus reached
%objective x. For instance
% A exploratory data analysis that shows the distribution of variables
% as well as a priori clusters is the first phase in any data
% processing method
% (BTW, you should include data visualization in problem description,
% because it shows the distribution of problem variables and then
% suggests ways to deal with it) - JJ
% and so on...

@@

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Moreover, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

@@

Feature extraction is a ``transformation-based approach'', therefore
it transforms the original meaning of the features. This approach
involves creating a subset of new features by combinations of the
existing features, thus it is employed when the semantics of the
original dataset will not be needed by any future process. On the
contrary, feature selection attempts to retain the meaning of the
original feature set. It is part of what is called semantic-preserving
techniques, known as ``selection-based approaches". By searching
through all possible combinations of features, the aim of these
techniques is to determine a minimal feature subset to reduce
processing time, while obtaining the same or higher accuracy as the
initial feature set \cite{liu1998feature}. In the problem this work
addresses, it is very important to maintain the semantics of the set of
initial variables, and therefore several feature selection methods
have been applied.

In addition, in order to reduce the dimensionality of the input data
and to choose an appropriate set of variables, the Self-Organizing Map
(SOM) \cite{kohonen1998} method has been also applied. % Why? Is that
                                % one of the two forms of feature
                                % selection? What do we expect to
                                % learn from it? - JJ

Kohonen's SOM is a feedforward neural network \cite{Haykin98_NNC} that
uses an unsupervised training algorithm and which, through a process
called self-organisation, configures the output units into a
topological representation of the original data. It tries to imitate
the self-organisation done in the sensory cortex of the human brain,
where neighbouring neurons are activated by similar stimulus. SOM
belongs to a general class of neural network methods, which are
non-linear regression techniques that can be trained to learn or find
relationships between inputs and outputs or to organise data so as to
disclose so far unknown patterns or structures. It is usually used as
a clustering/classification tool or used to find unknown relationships
between a set of variables that describe a problem. The main property
of the SOM is that it makes a nonlinear projection from a
high-dimensional data space (one dimension per variable) on a regular,
low-dimensional (usually 2D) grid of neurons, called units. 
SOM is further processed using Ultsch method \cite{UmatUlts}, the
Unified distance matrix (U-matrix), which uses SOM's codevectors
(vectors of variables of the problem) as data source and generates a
matrix where each component is a distance measure between two adjacent
neurons. It allows us to visualise any multi-variated dataset in a
two-dimensional display, so we can detect topological relations among
neurons and infer about the input data structure. High values in the
U-matrix represent a frontier region between clusters, and low values
represent a high degree of similarities among neurons on that region,
clusters .

SOMs (and U-Matrix) are usually applied to visualise natural
structures in the data and their relations, as well as the natural
groupings that could be among them. In addition, SOM makes easy the
estimation of the variables that have more influence on these
groupings. Other statistical and soft computing tools can also be used
for this purpose, but since Kohonen's SOMs offers a visual way of
doing it, it is much more intuitive, and takes advantage of the
capabilities of the human brain as a pattern recogniser. 
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?
% Antonio - arreglado 
% And this is going to be useful because... - JJ

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions (clusters) with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ
